\section{Appendices}

\subsection{Appendix A: Source Code Listings}

\texttt{main.m:}
\lstinputlisting[style=MatlabStyle]{../../src/rhythmic_inside/main.m}
\newpage

\texttt{calculateEnergy.m:}
\lstinputlisting[style=MatlabStyle]{../../src/rhythmic_inside/calculateEnergy.m}
\newpage

\texttt{autoCorrelation.m:}
\lstinputlisting[style=MatlabStyle]{../../src/rhythmic_inside/autoCorrelation.m}
\newpage

\texttt{detectPeaks.m:}
\lstinputlisting[style=MatlabStyle]{../../src/rhythmic_inside/detectPeaks.m}
\newpage

\texttt{calculateBPM.m:}
\lstinputlisting[style=MatlabStyle]{../../src/rhythmic_inside/calculateBPM.m}
\newpage

\texttt{config.m:}
\lstinputlisting[style=MatlabStyle]{../../src/rhythmic_inside/config.m}
\newpage

\texttt{customFilter.m:}
\lstinputlisting[style=MatlabStyle]{../../src/rhythmic_inside/customFilter.m}
\newpage

\texttt{processSignalForBPM.m:}
\lstinputlisting[style=MatlabStyle]{../../src/rhythmic_inside/processSignalForBPM.m}
\newpage

\texttt{recursiveFilter.m:}
\lstinputlisting[style=MatlabStyle]{../../src/rhythmic_inside/recursiveFilter.m}
\newpage

\texttt{selectWAV.m:}
\lstinputlisting[style=MatlabStyle]{../../src/rhythmic_inside/selectWAV.m}
\newpage

\subsection{Appendix B: References}

\begin{enumerate}
    \item Octave Documentation. (2024, March 4). Retrieved from \\ https://docs.octave.org/latest/
    \item SongBPM. (2024, March 4). Retrieved from \\ https://songbpm.com/
    \item Hills, M. (2024, March 1). BPM-Tools. Retrieved from \\ https://www.pogo.org.uk/~mark/bpm-tools/
    \item TIDAL. (2024, February 27). Top 100 Deutschland. Retrieved from \\ https://tidal.com/browse/playlist/56c28e48-5d09-4fb0-812e-c6c7c6647dcf
    \item Müller, M. (2024, February 28). Tempogram and Autocorrelation. Retrieved from \\ https://www.audiolabs-erlangen.de/resources/MIR/FMP/C6/ \\ C6S2\_TempogramAutocorrelation.html
\end{enumerate}
